Playing Atari Breakout with Keras and R

### 2018-07-13 article.Rmd
transform into radix article

---
title: "Playing Atari with Keras and R"
author: "Daniel Falbel and Fernando Barscevicius"
output: html_document
---

@@

With Gym we can also perform actions in the game by using the method `step`.

```{r}
result <- env$step(0L)
```

>>>>

---
title: "Playing Atari Breakout with Keras and R"
description: |
  In this article we will implement the famous paper from DeepMind: *Playing Atari 
  with Deep Reinforcement Learning* in R using Keras. This paper introduced the 
  first deep learning model that successfully learned control policies directly 
  from high-dimensional sensory input using reinforcement learning.
author:
  - name: Daniel Falbel 
    url: http://github.com/dfalbel
    affiliation: Curso-R
    affiliation_url: http://curso-r.com
  - name: Fernando Barscevicius
    url: 
    affiliation: Curso-R
    affiliation_url: http://curso-r.com
date: 07-17-2018
creative_commons: CC BY
repository_url: https://github.com/dfalbel/rl-keras
output: 
  radix::radix_article:
    self_contained: false
---

@@

With Gym we can also perform actions in the game by using the method `step`. We use the argument `action` to tell the environment which action to perform. Each different action is represented by an integer value.

```{r}
result <- env$step(action = 0L)
```

Gym does not document which action is performed by each integer value, but we can figure out by running actions in the emulator and looking at the rendered output. We can also get the number of possible actions by accessing the `env$action_space$n` member.

In our particular case, ie. the Atari Breakout game, there are 4 possible actions and the following table maps actions to corresponding integer values.

|
